### 2020-03-23 paper/intro.tex
Kills abstract, to-the-point intro, better title

@@

% \item We have designed \name, a novel fully decentralized, autonomous,
% and self-organizing file transfer service among users based on a novel
% concept named Stateless Probabilistic Onion Routes (SPOR), which combines onion routing with
% probabilistic node selection, informed by random peer sampling and
% predictions for node availability;
% \item We have extended Sphinx~\cite{Sphinx}, a compact and secure
%   message header format for mixnets, to allow for sets of nodes
%   instead of single nodes for onion routing layers, resulting in a
%   hybrid between source routing and ad-hoc node  selection that can
%   deal with unreliable nodes;
% \item  We have demonstrated the feasibility of our approach without
%   third-party storage, both in terms of security and performance . Even
%   suboptimal prediction results in successful file transfer with high
%   probability.

  \item We propose \Sphinxes, an extension of the
    Sphinx~\cite{Sphinx} mix-header format to set-based onion routing. \Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.

>>>>

First, we provide an extension to the Sphinx mix-header format~\cite{Sphinx} 
that adds several nodes per layer.
We call this extension SphinxES.
In essence, this makes it a source-routed random-walk.

The sender can populate the layers according to different optimizations.
For instance, the sender can populate the layers to minimize the risk of 
failure of a complete layer to minimize the impact of high churn in a 
network.
Another example is that the sender distribute nodes over the layers to maximize 
the sum of bandwidth over the nodes of each layer.
This would optimize for throughput.

Second, we provide a way for messaging services, like Signal, to use SphinxES 
to relay messages over the devices in \iac{P2P} network with high churn.
We call this the \ac{SPOR} protocol.

Third, we provide a higher-level protocol\footnote{%
  If SphinxES is IP, this protocol would be TCP.
} for file transfers.
We call this the \ac{SPORES} protocol.

\endinput

@@

% \item We have designed \name, a novel fully decentralized, autonomous,
% and self-organizing file transfer service among users based on a novel
% concept named Stateless Probabilistic Onion Routes (SPOR), which combines onion routing with
% probabilistic node selection, informed by random peer sampling and
% predictions for node availability;
% \item We have extended \ac{Sphinx}, a compact and secure
%   message header format for mixnets, to allow for sets of nodes
%   instead of single nodes for onion routing layers, resulting in a
%   hybrid between source routing and ad-hoc node  selection that can
%   deal with unreliable nodes;
% \item  We have demonstrated the feasibility of our approach without
%   third-party storage, both in terms of security and performance . Even
%   suboptimal prediction results in successful file transfer with high
%   probability.

  \item We propose \Sphinxes, an extension of the
    \ac{Sphinx} mix-header format to set-based onion routing. \Sphinxes allows each layer of an onion route to contain several alternative next nodes, thus realizing a source-routed limited random-walk protocol.
